School accessibility  in Sao Paulo

### 2015-09-24 paper.Rmd
Update abstract - 1st draft

Travel to school is an everyday reality for millions of young people around the world.
The mode, duration, levels

Access to high quality quality schools is highly variable across geographical
space so travel options are vital for ensuring a more equitable supply of
educational opportunity to diverse groups. Conversely, poor accessibility
to deprived area can reinforce social inequalities, with long-term implications.

Based on these emerging findings, this paper sets out a school accessibility index.
This index is based on current travel patterns, local travel infrastructure serving the school
catchment and the provision of travel services such as public transport links.
Using data from the Household Travel Survey (2007 and 2012), the School Census
and electronic card data, we apply this metric to schools in Sao Paulo.

Its impact on the social background of school attendees.
A wider aim of this paper is to explore the potential links between accessibility
and academic acheivement and opportunities.

# Introduction

Blah blah

>>>>

Travel to school is an everyday reality for millions of young people around the world.
The mode, duration, safety, comfort and pollution levels of this trip has huge
impacts on the future generation, yet has received relatively little academic
attention.
Access to high quality quality schools is highly variable across geographical
space, making travel options are vital for ensuring a more equitable supply of
educational opportunity to diverse groups. Conversely, poor accessibility
to deprived area can reinforce social inequalities, with long-term implications.
Based on this emerging context, this paper develops a school accessibility index
for local areas.
This index is based on current travel patterns, local travel infrastructure serving the school
catchment and the provision of travel services such as public transport links.
Using data from the Sao Paulo Household Travel Survey (2007 and 2012), School Census
and electronic card data, we demonstrate how this index can be used
measure current provision and evaluate future interventions.
The results suggest that that school accessibility can
impact the social background of school attendees and
academic performance.
We conclude that extending the concept of local accessibility indicators
to the 'school commute' can ensure that transport decision makers take
equality and health impacts on young people into account.
